Experience Report: Haskell in Computational Biology

### 2012-06-28 mrfy_experience_report.tex
fix bogus para break

Why have \texttt{pt0} and \texttt{nextPt}
instead 
of a single function with type \mbox{\texttt{Rand r [Scored pt]}},
which could produce an infinite list of points?
Because if the infinite list contains a useless point,

the starting point for the next move depends on whether the first move
was useful, whereas the first move is always useful.
That decision is made by the \texttt{utility} function,
which scrutinizes a move represented as follows:
\smallverbatiminput{move}
The decision about utility uses not only a source of randomness but
also the \emph{age} of the search, which corresponds to the
computational cost to reach a point in the search.
For example, in~simulated annealing, as the search progresses,
the \texttt{utility} function becomes less likely to express a move
that results in a worse score.

>>>>

Why have \texttt{pt0} and \texttt{nextPt}
instead 
of a single function with type \mbox{\texttt{Rand r [Scored pt]}},
which could produce an infinite list of points?
Because if the infinite list contains a useless point,
the starting point for the next move depends on whether the first move
was useful, whereas the first move is always useful.
That decision is made by the \texttt{utility} function,
which scrutinizes a move represented as follows:
\smallverbatiminput{move}
The decision about utility uses not only a source of randomness but
also the \emph{age} of the search, which corresponds to the
computational cost to reach a point in the search.
For example, in~simulated annealing, as the search progresses,
the \texttt{utility} function becomes less likely to express a move
that results in a worse score.
